---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```


```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSf_mAVF51_pdXGJLlDLyUKNxmZ2pCwSiJ6Q3wdy4hniwaw0opm3M204RG1jXsCLal3bd12jAab_HE-/pub?gid=775646179&single=true&output=csv")


#Renaming variables
latest_data <- logged_data %>% 
  rename(num_birds = 2,
         bird_type = 3,
         weather = 4,
         num_chirps = 5)

latest_data_longer <- latest_data %>% 
  separate_rows(bird_type, sep = ", ")

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Comic+Relief:wght@400;700&family=Oswald:wght@200..700&display=swap');

body {
      font-family: 'Comic Relief', cursive;
}

h1, h2, h3{
      color:#000000; background-color:#3177e8; padding:10px
}

h1, h2{
  font-weight: bold
  }

```

## Birds in the Back Garden

This data was collected by myself in my back garden at home in Sandringham. Whenever I felt like going outside, I would spend 30 seconds observing the garden looking for birds. I recorded the number of different birds I saw, the type of birds I saw, the number of bird chirps I heard, and the weather at the time of observation.

### Bar Charts

```{r}

ggplot(data = latest_data_longer) +
  geom_bar(aes(x = bird_type, fill = weather))+
  theme_minimal() +
  labs(title = "Bird type coloured by Weather at time of observation",
       subtitle = "Observed over 30s periods in my back garden",
       x = "Bird Type",
       fill = "Weather",
       y = "Count")

ggplot(data = latest_data_longer) +
  geom_bar(aes(x = num_birds, fill = bird_type))+
  theme_minimal() +
  labs(title = "Number of Birds Coloured by Type of Birds",
       subtitle = "Data collected over 30s periods, in my back garden",
       x = "Number of Birds",
       fill = "Type of Birds",
       y = "Count") 

```

### Dynamic Comments

```{r}
avg_chirps <- round(mean(latest_data$num_chirps, na.rm=TRUE), 2)

avg_birds <- round(mean(latest_data$num_birds, na.rm=TRUE), 2)

num_obs <- length(latest_data$Timestamp)

```
The average number of chirps heard across the `r num_obs` different 30 second periods observing the garden is `r avg_chirps`, and the average number of birds seen is `r avg_birds`. 